---
title: "logProbs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{logProbs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here we will show the basic usage of the logProbs package.

```{r setup, error=TRUE}
library(logProbs)

normalize_log_probs(c(-10, -10, -10))  # evaluate a standard log probability vector
normalize_log_probs(c(NA, -10, -10, -10), na.rm = TRUE)  # evaluate a standard log probability vector w/ NA
normalize_log_probs(c(-1000, -1000, -1000))  # evaluate numerically unstable log probability vector
```
We observe that `normalize_log_probs()` cannot deal with log probabilities with large magnitudes because this will create numerical overflow. Therefore, we need to use the stable version of the function `stable_normalize_log_probs()` as follows:

```{r}
stable_normalize_log_probs(c(-1000, -1000, -1000))  # evaluate numerically unstable log probability vector
```

To understand why this works look at the main README.md of the package under the proof section.
